\section{Goals}

The goal of our project is to implement a system with the following
functionality:

\begin{itemize}
\item Take a picture via a mobile device.
\item Detect faces in the acquired image and compute features for
  these faces.
\item Upload these features to a server and match them to indexed
  features of the user's friends' faces.
\item Extract relevant and interesting data from the matched user's
  profile on Facebook, Twitter, etc.
\item Send this information back to the phone for display, either in
  an overlaid or separate manner.
\end{itemize}



\section{Tools}

We plan to use OpenCV, the Facebook API, and as many other toolkits as
available.  We may use an available implementation of the Viola Jones
[1] face detector, perhaps the one available at
\code{http://www.cmucam.org/wiki/viola-jones}.



\section{Breakdown}

We plan on sharing the work initially, but moving as quickly as
possible to splittiing up the tasks.  Jason has a bit more experience
with web developement, and Cooper has done more with OpenCV, so we may
split the tasks along those lines.



\section{Special Equiptment}

Our project does not require much special equiptment.  We'll need to
use the phone for capturing images, as well as a server to store a
persistent index of facial features.  Any server could be used, but we
anticipate using a rented EC2 server from Amazon
(\code{http://aws.amazon.com/}).



\section{References}

[1] Viola, P. Jones, M.  ``Rapid Object Detection Using a Boosted
Cascade of Simple Features'', IEEE Computer Society Conference on
Computer Vision and Pattern Recognition, 2001, VOL 1, pages
I-511-I-518.
